Initial Analysis

### 2019-11-28 Initial_Analysis.Rmd
Included regional analysis as Colette suggested, still missing Catch

# Clean out countries that share with their own borders (e.g. Brazil mainland and Brazil (Fernando de Noronha))
  Auto_Remove_Territories <- Data %>% 
    filter(!is.na(Territory),
           !is.na(Neighbour)) %>% 
    rename(FishingRegion=Territory) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(TaxonKey,
           Territory= FishingRegion,
           FishingRegion=Neighbour, 
           Model_Index,
           Area_Index,
           CT_fishing_entity= fishing_entity) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(1,2, 
           Neighbour = FishingRegion,
           Model_Index:CT_fishing_entity,
           NT_fishing_entity= fishing_entity,
           everything()) %>% 
    mutate(
      CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Territory),paste(CT_fishing_entity)),
      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour),paste(NT_fishing_entity)),
      Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
    )

@@

# Species list to get species names
Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/Species/exploited_species_list.csv",sep=""))
Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/Species/SppTaxonName.csv",sep=""))

# Spatial Data needed to remove duplicates
sau_eez_fes <- fread(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep=""))

# UN Regions dataset
UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
  group_by(Territory = Country.or.Area,
           georegion = Region.Name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(Territory != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  # Change names to match SAU data and for shorter versions
  mutate(
    Territory = gsub("\\s*\\([^\\)]+\\)","",Territory),
    Territory = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",Territory),
    Territory = gsub( "United States of America", "USA",Territory),
    Territory = gsub("Democratic People's Republic of Korea", "Korea (North)",Territory),
    Territory = gsub("Republic of Korea", "Korea (South)",Territory),
    Territory = gsub("Iran (Islamic Republic of)", "Iran",Territory),
    Territory = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",Territory),
    # Territory = gsub("Congo", "Congo, R. of",Territory),
    Territory = gsub("United Republic of Tanzania", "Tanzania",Territory),
    Territory = gsub("Cabo Verde", "Cape Verde",Territory),
    Territory = gsub("Timor-Leste", "Timor Leste",Territory),
    Territory = gsub(" and ", " & ",Territory),
    # Territory = gsub("Puerto Rico (USA)", "Puerto Rico",Territory),
    Territory = gsub("Taiwan", "Taiwan (China)",Territory)
  )

@@

# Load it!
World_land_sf <- st_read(dsn = path_world_land,
                         layer =file_path_sans_ext(fnam_world_land)) %>% 
  rename(Territory = NAME)

@@

# Load it!
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(Territory = Name)

@@

# Read Sau Catch Data
SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
  filter(!is.na(Territory))

# Read Sau Value Data (Thank you Tim!)
SAU_Revenue_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
  group_by(fishing_entity_id,TaxonKey=taxon_key) %>% 
  summarise(Mean_Value = mean(value,na.rm=T))

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(Results_Path,"Species_Status.csv", sep =""))
# Status_Data <- Species_Status

@@

# Clean results susing function CleanResultsfun
Clean_Results_Trans <- CleanResults(Results_Trans)

# Load and clean Discrete results
Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep="")) %>% 
  filter(!is.na(TaxonKey)) %>% 
  select(2:3)

@@

Tresholded_T_Data <- Clean_Results_Trans %>% 
  filter(
    Area_Index >= Min_AI,
    Area_Index <= Max_AI,
    Model_Index >= MI
  )

### Non-transboundary Tresh 1
Clean_Non_Transboundary_Data <- Non_Transboundary_Data %>% 
  rename(eez_name = Territory) %>% 
  left_join(sau_eez_fes) %>% 
  group_by(Territory = fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey)),
            Taxons = paste(unique(TaxonKey),collapse = ";"))

## Determine as Trans. those species that are both trans and discrete for a nation (Tresh 2 and 3)
Tresholded_D_Data <- Clean_Results_Trans %>% 
  filter(Model_Index == MI) %>% 
  mutate(Species_Type = ifelse(Area_Index > Max_AI,"Discrete",
                               ifelse(Area_Index < Min_AI,NA,
                                      "Transboundary"))
  ) %>% 
  filter(!is.na(Species_Type)) %>% 
  group_by(CT_fishing_entity,Species_Type,TaxonKey) %>%
  summarise(n=n()) %>%
  spread(Species_Type,n) %>% 
  mutate(Discrete = ifelse(!is.na(Discrete) & !is.na(Transboundary),NA,Discrete)) %>% 
  gather("Species_Type","value", Discrete:Transboundary) %>% 
  filter(!is.na(value),
         Species_Type == "Discrete") %>% 
  group_by(Territory = CT_fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey)),
            Taxons = paste(unique(TaxonKey),collapse = ";")) %>% 
  #  Include discrete species of Trsh. 1
  bind_rows(Clean_Non_Transboundary_Data) %>%
  # Data cleaning (group by territory and include georegions for plot)
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(Territory = fishing_entity)

@@

Total_trans <- Clean_Results_Trans %>% 
  filter(
    Area_Index >= Min_AI,
    Area_Index <= Max_AI,
    Model_Index >= MI
  )

Total_trans_n <- Total_trans %>% 
  pull(TaxonKey) %>% 
  unique() %>% 
  length()

@@

Total_Trans_Rev <- SAU_Revenue_Data %>% 
  filter(TaxonKey %in% Total_trans$TaxonKey) %>% 
  group_by() %>% 
  summarise(Total =sum(Mean_Value)/1000000)# total revenue within EEZs of the world from sau.org

Per_Trans_Rev <- SAU_Revenue_Data %>% 
  filter(TaxonKey %in% Total_trans$TaxonKey) %>% 
  group_by() %>% 
  summarise(Total =sum(Mean_Value)/1000000) %>%  # million
  pull()/160000*100

@@

# Data per Territory
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(Territory) %>% 
  summarise(
    n_trans_spp = length(unique(TaxonKey)),
    n_Neighbours = length(unique(Neighbour)),
    Trans_Rate = n_trans_spp/n_Neighbours
  ) %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 4),
    Bins_Plot = cut(n_trans_spp,breaks = 4,
                    labels = c('super low', 'low', 'high','super high'))
  )

@@

Tresholded_T_Data_x <- Tresholded_T_Data %>% 
  select(TaxonKey, Territory=CT_fishing_entity)

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, Territory = fishing_entity) %>% 
  summarise(n=n()) %>% 
  select(-n) %>% 
  left_join(Tresholded_T_Data_x) %>% 
  left_join(Sau_Revenue_Data) %>% 
  group_by(Territory) %>% 
  summarise(Total_USD = (sum(Mean_Value,na.rm=T))/1000000) %>% # Million of USD
  mutate(Territory = ifelse(Territory == "USA","United States of America",Territory),
         Bins = cut(Total_USD,breaks = 4),
         Bins_Plot = cut(Total_USD,breaks = 4,
                         labels = c('super low', 'low','high','super high'))
  ) %>% 
  filter(Total_USD > 0)
```

@@

# Transboundary Species shapefile
World_sf_si <- World_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(Transboundary_Spp, by ="Territory")

# Total catch/Revenue shapefile
World_sf_si_land <- World_land_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  left_join(Revenue_Country, by ="Territory")

@@

# Make map
Plot <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,Total_USD)), colour = "grey80",size = 0.1) +
  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
  # rev(wes_palette(n = 4, name = "Darjeeling2"))
  # ),
  # na.value = "white"
  # ) +
  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                  "#00A08A",#"#00A08A", #green
                                  "#F2AD00",#"#F2AD00", # Yellow
                                  # "#F98400",#"#F98400", #Orange
                                  "#FF0000"#,"#FF0000" #Red
  ),
  na.value = "white"
  ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

>>>>

# Clean out countries that share with their own borders (e.g. Brazil mainland and Brazil (Fernando de Noronha))
  Auto_Remove_Territories <- Data %>% 
    filter(!is.na(Territory),
           !is.na(Neighbour)) %>% 
    rename(eez_name=Territory) %>% 
    left_join(Clean_sau_eez_fes,
              by = "eez_name") %>% 
    select(TaxonKey,
           Territory= eez_name,
           eez_name=Neighbour, 
           Model_Index,
           Area_Index,
           CT_fishing_entity= fishing_entity) %>% 
    left_join(Clean_sau_eez_fes,
              by = "eez_name") %>% 
    select(1,2, 
           Neighbour = eez_name,
           Model_Index:CT_fishing_entity,
           NT_fishing_entity= fishing_entity,
           everything()) %>% 
    mutate(
      CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Territory),paste(CT_fishing_entity)),
      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour),paste(NT_fishing_entity)),
      Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
    )

@@

# Species list to get species names
Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/Species/exploited_species_list.csv",sep="")) %>% 
  clean_names()

Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/Species/SppTaxonName.csv",sep="")) %>% 
  clean_names()

# Spatial Data needed to remove duplicates
sau_eez_fes <- fread(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep="")) %>% 
  clean_names()

Clean_sau_eez_fes <- sau_eez_fes %>% 
  gather("Type","fishing_region",2,4) %>% 
  left_join(sau_eez_fes,
            by = ("fishing_entity_id")
  ) %>% 
  group_by(eez_name,fishing_entity) %>% 
  summarise(n())

# UN Regions dataset
UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
  clean_names() %>% 
  group_by(fishing_entity = country_or_area,
           georegion = region_name,
           sub_region = sub_region_name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  # Change names to match SAU data and for shorter versions
  mutate(
    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity)
  )

@@

# Load it!
World_land_sf <- st_read(dsn = path_world_land,
                         layer =file_path_sans_ext(fnam_world_land)) %>% 
  rename(fishing_entity = NAME)

@@

# Load it!
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name)

@@

# Read Sau Catch Data
# SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
  # filter(!is.na(Territory))

# Read Sau Value Data (Thank you Tim!)
SAU_Revenue_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
  clean_names() %>% 
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise(mean_value = mean(value,na.rm=T))

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(Results_Path,"Species_Status.csv", sep ="")) %>% 
  clean_names()
# Status_Data <- Species_Status

@@

# Clean results susing function CleanResultsfun
Clean_Results_Trans <- CleanResults(Results_Trans) %>% 
  clean_names() %>% 
  rename(eez_name = territory,
         fishing_entity = ct_fishing_entity,
         eez_neighbour = neighbour)

# Load and clean Discrete results
# Non_Transboundary_Data <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep="")) %>% 
#   filter(!is.na(TaxonKey)) %>% 
#   select(2:3)

@@

Tresholded_T_Data <- Clean_Results_Trans %>% 
  filter(
    area_index >= Min_AI,
    area_index <= Max_AI,
    model_index >= MI
  )

### Non-transboundary Tresh 1
# Clean_Non_Transboundary_Data <- Non_Transboundary_Data %>% 
#   rename(eez_name = Territory) %>% 
#   left_join(sau_eez_fes) %>% 
#   group_by(Territory = fishing_entity) %>% 
#   summarise(value = length(unique(TaxonKey)),
#             Taxons = paste(unique(TaxonKey),collapse = ";"))

## Determine as Trans. those species that are both trans and discrete for a nation (Tresh 2 and 3)
# Tresholded_D_Data <- Clean_Results_Trans %>% 
#   filter(Model_Index == MI) %>% 
#   mutate(Species_Type = ifelse(Area_Index > Max_AI,"Discrete",
#                                ifelse(Area_Index < Min_AI,NA,
#                                       "Transboundary"))
#   ) %>% 
#   filter(!is.na(Species_Type)) %>% 
#   group_by(CT_fishing_entity,Species_Type,TaxonKey) %>%
#   summarise(n=n()) %>%
#   spread(Species_Type,n) %>% 
#   mutate(Discrete = ifelse(!is.na(Discrete) & !is.na(Transboundary),NA,Discrete)) %>% 
#   gather("Species_Type","value", Discrete:Transboundary) %>% 
#   filter(!is.na(value),
#          Species_Type == "Discrete") %>% 
#   group_by(Territory = CT_fishing_entity) %>% 
#   summarise(value = length(unique(TaxonKey)),
#             Taxons = paste(unique(TaxonKey),collapse = ";")) %>% 
#   #  Include discrete species of Trsh. 1
#   bind_rows(Clean_Non_Transboundary_Data) %>%
#   # Data cleaning (group by territory and include georegions for plot)
#   rename(FishingRegion=Territory) %>% 
#   left_join(Clean_sau_eez_fes) %>% 
#   group_by(Territory = fishing_entity)

@@

Total_trans <- Clean_Results_Trans %>% 
  filter(
    area_index >= Min_AI,
    area_index <= Max_AI,
    model_index >= MI
  )

Total_trans_n <- Total_trans %>% 
  pull(taxon_key) %>% 
  unique() %>% 
  length()

@@

Total_Trans_Rev <- SAU_Revenue_Data %>% 
  filter(taxon_key %in% Total_trans$taxon_key) %>% 
  group_by() %>% 
  summarise(Total =sum(mean_value)/1000000)# total revenue within EEZs of the world from sau.org

Per_Trans_Rev <- SAU_Revenue_Data %>% 
  filter(taxon_key %in% Total_trans$taxon_key) %>% 
  group_by() %>% 
  summarise(Total =sum(mean_value)/1000000) %>%  # million
  pull()/160000*100

@@

# Data per Territory
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_name) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 4),
    Bins_Plot = cut(n_trans_spp,breaks = 4,
                    labels = c('super low', 'low', 'high','super high'))
  )

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% 
  select(-n) %>% 
  full_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% 
  left_join(SAU_Revenue_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity) %>% 
  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",fishing_entity),
         Bins = cut(Total_USD,breaks = 4),
         Bins_Plot = cut(Total_USD,breaks = 4,
                         labels = c('super low', 'low','high','super high'))
  ) %>% 
  filter(Total_USD > 0)

```{r Data_per_Continent, eval = F, echo = F}

Continent_Data <- Revenue_Country %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region) %>% 
  summarise_if(is.numeric,sum,na.rm=T)

Continent_Data_Trans <- Tresholded_T_Data %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key))
  ) %>% 
  left_join(Continent_Data) %>% 
  mutate(id = seq(1,nrow(Continent_Data_Trans)))

### Prepare data for plot

number_of_bar <- nrow(Continent_Data_Trans)

label_data <- Continent_Data_Trans %>% 
  arrange(Total_USD) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Continent_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Latin America &\nthe Caribbean",paste(sub_region))
  )

@@

# Transboundary Species shapefile
World_sf_si <- World_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(Transboundary_Spp, by ="eez_name")

# Total catch/Revenue shapefile
World_sf_si_land <- World_land_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  left_join(Revenue_Country, by ="fishing_entity")

@@

# Make map
Map <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,Total_USD)), colour = "grey80",size = 0.1) +
  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
  # rev(wes_palette(n = 4, name = "Darjeeling2"))
  # ),
  # na.value = "white"
  # ) +
  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                  "#00A08A",#"#00A08A", #green
                                  "#F2AD00",#"#F2AD00", # Yellow
                                  # "#F98400",#"#F98400", #Orange
                                  "#FF0000"#,"#FF0000" #Red
  ),
  na.value = "white"
  ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

####___________________________###
### Now create the Two circluar bar plots
####___________________________###

# Revenue Plot
# Set plot limits
min_lim <- min(Continent_Data_Trans$Total_USD)
max_lim <-max(Continent_Data_Trans$Total_USD)

# Set color pal
pal <- wes_palette("Zissou1",100,type = "continuous")

Rev_Plot <- ggplot(data = Continent_Data_Trans, 
       aes(x=reorder(id,Total_USD),
           y=Total_USD, 
           fill=Total_USD
           )
       ) +    
  ylim(-1500, max_lim+10)+
  geom_bar(stat="identity") +
  theme_minimal() +
  theme(
    # legend.position = c(0.80,0.50),
    legend.position = "",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-5,-10,"cm")
  )  +
  # Base line
  geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
               colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data, 
            aes(x=id,
                y=Total_USD+10,
                # label=round(Total_USD_Billion),
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("Billion USD",
                       colours = pal)

### Catch plot

Catch_Plot <- ggplot(data = Continent_Data_Trans, 
       aes(x=reorder(id,Total_USD),
           y=Total_USD, 
           fill=Total_USD
           )
       ) +    
  ylim(-1500, max_lim+10)+
  geom_bar(stat="identity") +
  theme_minimal() +
  theme(
    # legend.position = c(0.80,0.50),
    legend.position = "",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-5,-10,"cm")
  )  +
  # Base line
  geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
               colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data, 
            aes(x=id,
                y=Total_USD+10,
                # label=round(Total_USD_Billion),
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("Tons",
                       colours = pal)

## Joining everything in one ploit

# library(ggpubr)
# library(cowplot)

plot <- ggdraw() +
  # map
  draw_plot(Map, x = 0, y = 0.4, width = 1, height = 0.6) +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0.05, y = 0.1, width = 0.5, height = 0.4) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.5, y = 0.1, width = 0.5, height = 0.4) +

  # Labeks
  draw_plot_label(label = c("A", "B", "C"), 
                  size = 30,
                  x = c(0.1, 0.1, 0.56), 
                  y = c(1, 0.45, 0.45)
  )

save_plot("Plot2.png",
          plot,
          base_height = 8,
          base_width = 13)
